Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-04 prop.tex
prop.tex \section{Conclusion and Discussion} Updating table...

$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline

@@

\end{tabular}}\caption{How measurement resources effect identifying states from interval-valued
probability measures.}

@@

Although the tend is clear, we still need more examples to fill the
blank and to prove our idea. Some research questions might be

>>>>

$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline

@@

\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}

@@

According to table~\ref{table_long}, when we increase the measurement
resources, interval-valued probability measures could more and more
likely be identified to a particular state. Although the tend is clear,
there are still a lot of questions need to be answered, including: 
